\documentclass[11pt, a4paper]{moderncv}

\moderncvtheme[green]{classic}

\usepackage[scale=0.90]{geometry}
\recomputelengths                            

\firstname {Alexander}
\familyname {Demidenko}

\title{Software Developer}

\address{United Kingdom}
\mobile{Tel: +44 7770 625-327}   
\email{Email: kibarabara@gmail.com} 

\begin{document}
 
\maketitle

\section{Experience}

\cventry{Aug 2013-present}{Geophysical Software Developer}{ARK CLS LTD}{}{Bedford, UK}
{
Working on various geophysical software; 
developing UI using Qt Widgets and implementing calculation algorithms; 
designing applications architecture and solutions.
}

\cventry{Mar 2013 - Apr 2013}{Software Developer}{SecurityCode}{}{Moscow, Russia}
{
I started as iOS/C++ maintainer/developer of secure VPN client.
Made automatic-build environment for building iOS client and closed several outstanding issues.
}

\cventry{Mar 2012 - Feb 2013}{Software Developer}{OJSC MTT}{}{Moscow, Russia}
{
Initially I started as Desktop/Qt leader for MTT YouMagic client but after the first month I was asked to temporarily join the iOS mobile team where  
I learned Objective-C and essentials of the iOS. There I was contributing greatly to different parts of the mobile client and architecture solutions.
Several months later I picked back up Desktop/Qt leadrship and started to maintain and manage small outsource team 2-5 people. 
As a result of our work YouMagic Linux Desktop client became a part of Linux ROSA distributive.
Along with completing this goal our team was able to successfully create releases for other platforms such as Windows 7 and various Linux distributives.
}

\cventry{Sep 2010 - Oct 2011}{Software Developer}{ScienceSoft}{}{Minsk, Belarus}
{
In 2010 I moved to Belarus and joined pretty big outsourcing company placed in Minsk. 
There I started as C++ developer and started to learn Qt technology and became a big fun of it.
Several months later I joined growing Viber mobile client team and I've been porting sound engine from iOS into Android. 
Touched NDK/JNI technologies and successfully accomplished porting.
Later I was temporarily maintaining and developing fTalk client and right after joined Viber PC team and started to work on Desktop client.
I was responsible for developing various parts of GUI client along with making improvements to existingapplication engine.
}

\cventry{Oct 2009 - Aug 2010}{Software Developer}{Moscow Institute of Radiotechnics}{}{Moscow, Russia}
{
aaa
}

\cventry{Jan 2008 - Aug 2009}{Software Developer}{Moscow Institute of Space Device Engineering}{}{Moscow, Russia}
{
aa
}

\section{Education}

\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
 
 
\end{document}

 